---
title: "User-Clustering"
author: "Surya Balakrishnan Ramakrishnan"
date: "16/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## User clustering for people who have selected shops in the Buttercrane

```{r, message=FALSE, warning=FALSE, echo=TRUE}
#Folder in the desktop
library(cluster)
library(dplyr)
library(ggplot2)
library(readr)
library(Rtsne)
library(factoextra)
library(readxl)
library(biganalytics)
library(RPostgres)
library(stringi)
library(knitr)
library(plotly)
```

```{r}
setwd("C:/Users/3054863/Desktop/data science/clustering-insights")
```



## Sample Data from the database.

```{r, echo=FALSE}
con2 <- dbConnect(RPostgres::Postgres(), 
                  host="pearlai-prod.cquyrubqha9e.eu-west-1.rds.amazonaws.com", 
                  dbname="spiritsoft",
                  user = "surya",
                  password = stri_enc_toutf8("Ramkisurya7$"))
                  #user= "Read-Only",
                  #password= stri_enc_toutf8("7UY765T*£Y6Tybvc!"))
```


```{r}
res <- dbSendQuery(con2, "

SELECT  profile_id
     ,demograph_id
     , dp.gender
     , dp.age_group
     , dp.no_children
     , CASE
         WHEN dp.shopping_frequency = 1 THEN 'Everyday'
         WHEN dp.shopping_frequency = 2 THEN 'Every Week'
         WHEN dp.shopping_frequency = 3 THEN 'Every Two Weeks'
         WHEN dp.shopping_frequency = 4 THEN 'Every Month'
         WHEN dp.shopping_frequency = 5 THEN 'Every Three Months'
             ELSE NULL
        END AS shopping_frequency
     , dp.marital_status
     , dp.employment_status
FROM (
SELECT DISTINCT profile_id,demograph_id
FROM common.profile_whitelist wl
LEFT JOIN common.customer cc
ON wl.customer_id = cc.id
RIGHT JOIN common.profile cp
ON wl.profile_id = cp.uuid
where cc.centre_id = 6
)active_users
LEFT JOIN common.demograph_permutations dp
ON active_users.demograph_id = dp.id;
                   ")
profiles <- dbFetch(res)
dbClearResult(res)
write.csv(profiles, "profiles.csv")
DT::datatable(head(profiles))
```


```{r}
res <- dbSendQuery(con2, paste("

select profile_id, customer_id, cn.cust_name
from common.profile_whitelist wl
left join common.customer cn
on wl.customer_id = cn.id
where cn.is_active is TRUE and wl.profile_id in (", paste0(profiles$profile_id, collapse = ","), ");
                   "), sep = "")

shop_selection <- dbFetch(res)
dbClearResult(res)
write.csv(shop_selection, "shop_selection.csv")
DT::datatable(head(shop_selection))
```


```{r}
res <- dbSendQuery(con2, paste("

select date(start_time), profile_id, customer_id, duration/60 dwell_mins
from rollups.centre_tenant_visitor
where profile_id in (", paste0(profiles$profile_id, collapse = ","), ") and date(start_time) >= '2019-11-01' and date(start_time) <= '2020-01-31';
                   "), sep = "")

visits <- dbFetch(res)
dbClearResult(res)
write.csv(visits, "visits.csv")
DT::datatable(head(visits))
```

```{r}
res <- dbSendQuery(con2, paste("

select date(sent.text_sent_at), sent.client_report_id,  sent.customer_id, sent.cust_name, conv.converted_at
from(
    select text_sent_at, client_report_id, tc.customer_id, tn.cust_name
    from rollups.centre_tenant_conversions tc
    left join common.customer tn
    on tc.customer_id = tn.id
    where date(text_sent_at) >= '2019-11-01' and date(text_sent_at) <= '2020-01-31' and profile_id in (", paste0(profiles$profile_id, collapse = ","), ")
        )sent
left join (
    select * from rollups.centre_tenant_conversions
    where date(text_sent_at) >= '2019-11-01' and date(text_sent_at) <= '2020-01-31' and converted_at != '-infinity'and profile_id in and profile_id in (", paste0(profiles$profile_id, collapse = ","), ")
    )conv
on sent.client_report_id = conv.client_report_id; and date(start_time) >= '2019-11-01' and date(start_time) <= '2020-01-31';
                   "), sep = "")

conversions <- dbFetch(res)
dbClearResult(res)
#write.csv(visits, "visits.csv")
DT::datatable(head(conversions))

```


## Profile Composition

```{r}
profiles[is.na(profiles)] <- "NA"
profiles$demograph_id <- as.factor(profiles$demograph_id)
profiles$gender <- as.factor(profiles$gender)
profiles$age_group <- as.factor(profiles$age_group)
profiles$no_children <- as.factor(profiles$no_children)
profiles$shopping_frequency <- as.factor(profiles$shopping_frequency)
profiles$marital_status <- as.factor(profiles$marital_status)
profiles$employment_status <- as.factor(profiles$employment_status)
summary(profiles)
```





```{r}
#Conversion of catagorical data to numaric by computing the GOWER Distance Computes the measure of dissimilarities
  gower_dist <- daisy(profiles, metric = c("gower"))
  #Converting the GOVER distance as a matrix 
  gower_mat <- as.matrix(gower_dist)
```


```{r}
library(Gifi)
fitord <- princals(profiles[,c(3:8)])
```


```{r, warning=FALSE}
fitord
summary(fitord)

plot(fitord, plot.type = "transplot")
plot(fitord, "loadplot", main = "Loadings Plot")  ## aspect ratio = 1
plot(fitord, "biplot", labels.scores = TRUE, main = "") #Biplot User Data
plot(fitord, "screeplot")
```





## K-Means Clustering

Current Clustering methodology to be implemented in the buttercrane shopping centre

Number of clusters = 5, number of number of iterations (starting point permutations) 5000
```{r}
#nstart needs to be set at 5000, once the demographic data has been made accurate.
km.res <- bigkmeans(gower_mat, 5, nstart = 50)
```

## Cluster plot factor
```{r}
fviz_cluster(km.res, data = gower_mat,
              ellipse.type = "convex",
              palette = "jco",
              ggtheme = theme_minimal())
```



## Cluster plot factor
```{r}
#Finds distance between catagorical variables of two columns 
plot(profiles[,1:8],col=km.res$cluster)
#fviz_cluster(km.res, data = gower_mat,
#              ellipse.type = "convex",
#              palette = "jco",
#              ggtheme = theme_minimal())
```


```{r}
cluster_data <- profiles %>%
  mutate(cluster = km.res$cluster) %>%
  group_by(cluster)

```


```{r}
DT::datatable(head(cluster_data))
```


```{r}
cluster1 <- cluster_data[cluster_data[,9] == 1,]
cluster2 <- cluster_data[cluster_data[,9] == 2,]
cluster3 <- cluster_data[cluster_data[,9] == 3,]
cluster4 <- cluster_data[cluster_data[,9] == 4,]
cluster5 <- cluster_data[cluster_data[,9] == 5,]
```

## Cluster Composition

```{r}
summary(cluster1)
```

```{r}
summary(cluster2)
```

```{r}
summary(cluster3)
```

```{r}
summary(cluster4)
```

```{r}
summary(cluster5)
```

```{r, echo=FALSE, eval=FALSE}
smp_size <- floor(0.50 * nrow(cluster1))
set.seed(123)
index <- sample(seq_len(nrow(cluster1)), size = smp_size)
treatment1 <- cluster1[index, ]
placebo1 <- cluster1[-index,]
```

```{r, echo=FALSE, eval=FALSE}
smp_size <- floor(0.50 * nrow(cluster2))
set.seed(123)
index <- sample(seq_len(nrow(cluster2)), size = smp_size)
treatment2 <- cluster2[index, ]
placebo2 <- cluster2[-index,]
```

```{r, echo=FALSE, eval=FALSE}
smp_size <- floor(0.50 * nrow(cluster3))
set.seed(123)
index <- sample(seq_len(nrow(cluster3)), size = smp_size)
treatment3 <- cluster3[index, ]
placebo3 <- cluster3[-index,]
```

```{r, echo=FALSE, eval=FALSE}
smp_size <- floor(0.50 * nrow(cluster4))
set.seed(123)
index <- sample(seq_len(nrow(cluster4)), size = smp_size)
treatment4 <- cluster4[index, ]
placebo4 <- cluster4[-index,]
```

```{r, echo=FALSE, eval=FALSE}
smp_size <- floor(0.50 * nrow(cluster5))
set.seed(123)
index <- sample(seq_len(nrow(cluster5)), size = smp_size)
treatment5 <- cluster5[index, ]
placebo5 <- cluster5[-index,]
```

```{r}
merged_treatment <- rbind(treatment1,treatment2,treatment3,treatment4,treatment5)
merged_placebo <- rbind(placebo1,placebo2,placebo3,placebo4,placebo5)
```


```{r, echo=FALSE, eval=FALSE}
#Write CSV Statements to be pushed out
write.csv(cluster_data, 'profiles.csv')
write.csv(merged_treatment, 'treatment.csv')
write.csv(merged_placebo, 'placebo.csv')

write.csv(profiles, 'profiles.csv')
write.csv(cluster1, 'cluster1.csv')
write.csv(cluster2, 'cluster2.csv')
write.csv(cluster3, 'cluster3.csv')
write.csv(cluster4, 'cluster4.csv')
write.csv(cluster5, 'cluster5.csv')
write.csv(treatment1, 'treatment1.csv')
write.csv(treatment2, 'treatment2.csv')
write.csv(treatment3, 'treatment3.csv')
write.csv(treatment4, 'treatment4.csv')
write.csv(treatment5, 'treatment5.csv')
write.csv(placebo1, 'placebo1.csv')
write.csv(placebo2, 'placebo2.csv')
write.csv(placebo3, 'placebo3.csv')
write.csv(placebo4, 'placebo4.csv')
write.csv(placebo5, 'placebo5.csv')
```

```{r, echo=FALSE, eval=FALSE}
res <- dbSendQuery(con2, paste("

select ad_id, customer_id, count(ad_id) conversions
    from rollups.centre_tenant_conversions
    where
    text_sent_at between '2020-01-01' and '2020-01-31'
    and centre_id = 6
    and profile_id in(",paste0(treatment1$profile_id, collapse = ","),")
    group by ad_id, customer_id
    order by conversions DESC;
                   ", sep = ""))


message1 <- dbFetch(res)
dbClearResult(res)
DT::datatable(head(message1))
```

```{r, echo=FALSE, eval=FALSE}
res <- dbSendQuery(con2, paste("

select ad_id, customer_id, count(ad_id) conversions
    from rollups.centre_tenant_conversions
    where
    text_sent_at between '2020-01-01' and '2020-01-31'
    and centre_id = 6
    and profile_id in(",paste0(treatment2$profile_id, collapse = ","),")
    group by ad_id, customer_id
    order by conversions DESC;
                   ", sep = ""))


message2 <- dbFetch(res)
dbClearResult(res)
DT::datatable(head(message2))
```

```{r, echo=FALSE, eval=FALSE}
res <- dbSendQuery(con2, paste("

select ad_id, customer_id, count(ad_id) conversions
    from rollups.centre_tenant_conversions
    where
    text_sent_at between '2020-01-01' and '2020-01-31'
    and centre_id = 6
    and profile_id in(",paste0(treatment3$profile_id, collapse = ","),")
    group by ad_id, customer_id
    order by conversions DESC;
                   ", sep = ""))


message3 <- dbFetch(res)
dbClearResult(res)
DT::datatable(head(message3))
```

```{r, echo=FALSE, eval=FALSE}
res <- dbSendQuery(con2, paste("

select ad_id, customer_id, count(ad_id) conversions
    from rollups.centre_tenant_conversions
    where
    text_sent_at between '2020-01-01' and '2020-01-31'
    and centre_id = 6
    and profile_id in(",paste0(treatment4$profile_id, collapse = ","),")
    group by ad_id, customer_id
    order by conversions DESC;
                   ", sep = ""))


message4 <- dbFetch(res)
dbClearResult(res)
DT::datatable(head(message4))
```

```{r, echo=FALSE, eval=FALSE}
res <- dbSendQuery(con2, paste("

select ad_id, customer_id, count(ad_id) conversions
    from rollups.centre_tenant_conversions
    where
    text_sent_at between '2020-01-01' and '2020-01-31'
    and centre_id = 6
    and profile_id in(",paste0(treatment5$profile_id, collapse = ","),")
    group by ad_id, customer_id
    order by conversions DESC;
                   ", sep = ""))


message5 <- dbFetch(res)
dbClearResult(res)
DT::datatable(head(message5))
```

```{r}
message1$cluster_id <- 1
message2$cluster_id <- 2
message3$cluster_id <- 3
message4$cluster_id <- 4
message5$cluster_id <- 5
merged_message <- rbind(message1,message2,message3,message3,message4,message5)
```


```{r, echo=FALSE, eval=FALSE}
#Write CSV Statements to be pushed out
write.csv(merged_message, 'messages.csv')
write.csv(message1,'message1.csv')
write.csv(message2,'message2.csv')
write.csv(message3,'message3.csv')
write.csv(message4,'message4.csv')
write.csv(message5,'message5.csv')
```

